The minimal nucleosynthesis project with \apogee

### 2016-04-01 papers/nucleosynthesis/nuke.tex
abstract and dex

% # to-do list
% - fix prior on the \epsilon_{kd} to make everything normal in the log!

@@

\begin{abstract}
We describe the minimal thing you could do with the \apogee\ data to
improve our understanding of nucleosynthesis.
\end{abstract}

@@

We adopt the standard terminology, that an abundance in square brackets
is taken to be log (base 10) and relative to Solar:
\begin{eqnarray}
  \abundance{X/Y}_n &\equiv& \log_{10}\left(\left.\frac{X}{Y}\right|_n\right) -
                             \log_{10}\left(\left.\frac{X}{Y}\right|_\solar\right)
\quad ,
\end{eqnarray}
where the index $n$ indicates the identity (\apogee\ label) of the star.
Our model obtains some complexity, because we assume (unrealistically)
that the uncertainties are Gaussian in the log (base 10) but our
nucleosynthetic model will be linear in the linear abundance ratios.
In particular, we assume that each logarithmic abundance $\abundance{X/Y}$
can be written as the log (base 10) of a linear abundance ratio $y$ with
an error applied (outside the log)
\begin{eqnarray}
  \abundance{X/Y}_n &=& \log_{10}(y_{nd}) + e_{nd} \label{eq:model1}
\\
  p(e_{nd}) &=& \normal(e_{nd}\given 0,\sigma^2_{nd}) \label{eq:model2}
\quad ,
\end{eqnarray}
where the index $n$ indicates the star and the index $d$ indicates the
particular abundance ratio (for example, $\abundance{\element{Fe}/\element{H}}$ might get
$d=1$, and $\abundance{\element{C}/\element{Fe}}$ might get $d=2$, and so on), $y_{nd}$ is
the linear abundance ratio as given by the nucleosynthetic mean model
prediction (see below), and $e_{nd}$ is an error drawn from a Gaussian
frequency distribution with zero mean and known variance $\sigma^2_{nd}$.

>>>>

% # to-do list
% - put in figures showing the G vectors.

@@

\begin{abstract}
We describe the minimal thing you could do with the \apogee\ data to
improve our understanding of nucleosynthesis:
Model the detailed distribution of stars in 15-dimensional abundance
space as a non-negative mixture of supernova and AGB yield vectors,
but permitting those yield vectors to be distorted where the data
require it.
\end{abstract}

@@

We adopt the standard terminology, that an abundance in square brackets
is taken to be log (base 10) and relative to Solar:
\begin{eqnarray}
  \abundance{X/Y}_n &\equiv& \log_{10}\left(\left.\frac{X}{Y}\right|_n\right) -
                             \log_{10}\left(\left.\frac{X}{Y}\right|_\solar\right)
\quad ,
\end{eqnarray}
where the index $n$ indicates the identity (\apogee\ label) of the star.
Our model obtains some complexity, because we assume (unrealistically)
that the uncertainties are Gaussian in the log (base 10) but our
nucleosynthetic model will be linear in the linear abundance ratios.
In particular, we assume that each logarithmic abundance $\abundance{X/Y}$
can be written as the log (base 10) of a linear abundance ratio $y$ with
an error applied (outside the log)
\begin{eqnarray}
  \abundance{X/Y}_n &=& \log_{10}(y_{nd}) + e_{nd} \label{eq:model1}
\\
  p(e_{nd}) &=& \normal(e_{nd}\given 0,\sigma^2_{nd}) \label{eq:model2}
\quad ,
\end{eqnarray}
where the index $n$ indicates the star and the index $d$ indicates the
particular abundance ratio (for example, $\abundance{\element{Fe}/\element{H}}$ might get
$d=1$, and $\abundance{\element{C}/\element{Fe}}$ might get $d=2$, and so on), $y_{nd}$ is
the linear abundance ratio as given by the nucleosynthetic mean model
prediction (see below), and $e_{nd}$ is an error (in dex) drawn from a Gaussian
frequency distribution with zero mean and known variance $\sigma^2_{nd}$.
